Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-02-03 Journal1/paper2TNSM/pr.tex
add some questions

Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
%Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)

To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
\begin{equation}\label{eq2}
y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}\mathfrak{y}^k_{r,u(s,i)}+ z_{u(s,i)},
\end{equation}
%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}
where $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$, $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization Gaussian noise 
($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as
\begin{equation}\label{eq3}
\begin{split}
\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)},
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission, the achievable data rate is approximated from following \cite{setayesh2020joint},
\begin{subequations}\label{eq11}
\begin{alignat}{4}
\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
\end{alignat}
\end{subequations}
where %$j \in \{2,3\}$. Also we have $ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}},$.
%{\color{red} check paranthesis. }
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}, 
\end{equation}
%{\color{red} what is transmission probability? }
where $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.

@@

So, the mean processing delay for UE $i$ in slice $s$ is $T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.$
%\begin{equation}
%T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
%\end{equation}
Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. %{\color{red} what results in this approximation?}
%Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).  
\subsection{VNF Power}
%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} 
Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.

>>>>

Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
%Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ \textcolor{teal}{is the sum of the power of interfering signals and quantization noise represented as follow}
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)

\textcolor{teal}{To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service formulated as
\begin{equation}\label{eq2}
y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}{x_Q}^k_{r,u(s,i)}+ z_{u(s,i)},
\end{equation}
}
%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}  $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
\textcolor{teal}{where ${x_Q}^k_{r,u(s,i)} ={x_P}^k_{r,u(s,i)}+ \boldsymbol{q}_{r}$. Also, ${x_P}^k_{r,u(s,i)}= \boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)} $, and  $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression that is shown in figure \ref{fig:pq}. 
In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization Gaussian noise 
($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.}
\begin{figure}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.45]{Qdiag.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Precoding and Quantization of Signal}
  \label{fig:pq}
\end{figure}
The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as
\begin{equation}\label{eq3}
\begin{split}
\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)},
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission, the achievable data rate is approximated from following \cite{setayesh2020joint},
\begin{subequations}\label{eq11}
\begin{alignat}{4}
\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
\end{alignat}
\end{subequations}
where %$j \in \{2,3\}$. Also we have $ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}},$.
%{\color{red} check paranthesis. }
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}, 
\end{equation}
%{\color{red} what is transmission probability? }
where $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.

@@

So, the mean processing delay for UE $i$ in slice $s$ is $T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.$
%\begin{equation}
%T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
%\end{equation}
Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $. %{\color{red} what results in this approximation?}
%Furthermore, the mean arrival data rate of the each link ($\textstyle \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$) is approximately equal to others ($\textstyle \alpha_{s} \approx \alpha_{s}^i$ , $i \in \{RU,DU,CU,UPF\}$).

\textcolor{olive}{The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent. Moreover, the impact of a single packet on the system's performance is minimal. Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process. We also suppose that service times are exponentially distributed. In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services. Because in this system, it is also assumed that the users of a service have the same priority, so their sent packages also have an equal priority over each other. Because the services are isolated, this priority within a service does not invalidate the queue assumption. Also, one service's priority over another can be higher, affecting the optimization.} 
\subsection{VNF Power}
%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} 
Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.
